A Type System for Safe and Scalable Parallelism using Logical Regions \\ (Extended Version)

### 2012-07-20 doc/popl2013full/langdef.tex

Similarly, observe that
$$\hat \Omega_1 [ \rho_1/r'_1,\ldots,\rho_k/r'_k ] = M \llbracket \Omega_1 [ r_1/r'_1,\ldots,r_k/r'_k ] \rrbracket$$
.  With two applications of Lemma~\ref{lemma:mappedomega}, we have
$$\mapconsist[\{(r'_i,\rho_i)\}]{\hat \Omega_1} \Leftrightarrow \mapconsist{\Omega_1 [ r_1/r'_1,\ldots,r_k/r'_k ]}$$
.  The latter constraints are a subset of
$\Omega^*$, and must be satisfied if $\mapconsist{\Omega^*}$, which we have from Lemma~\ref{lemma:omegaclosure}.

>>>>

Similarly, observe that
$$\hat \Omega_1 [ \rho_1/r'_1,\ldots,\rho_k/r'_k ] = M \llbracket \Omega_1 [ r_1/r'_1,\ldots,r_k/r'_k ] \rrbracket$$
With two applications of Lemma~\ref{lemma:mappedomega}, we have
$$\mapconsist[\{(r'_i,\rho_i)\}]{\hat \Omega_1} \Leftrightarrow \mapconsist{\Omega_1 [ r_1/r'_1,\ldots,r_k/r'_k ]}$$
The latter constraints are a subset of
$\Omega^*$, and must be satisfied if $\mapconsist{\Omega^*}$, which we have from Lemma~\ref{lemma:omegaclosure}.
